???A quantitative framework for investigating the reliability of network construction

### 2017-09-17 manuscript/CI_interactions.tex
more changes

\author{Dominique Gravel, D. Carstensen, Timoth\'{e}e Poisot, Daniel B. Stouffer, \& Alyssa R. Cirtwill$^{1}$, others??}
\date{\small$^1$Department of Physics, Chemistry\\ 
and Biology (IFM)\\ 
Link\"{o}ping University\\
Link\"{o}ping, Sweden\\
% \medskip
% $^\dagger$ Corresponding author:\\
% alyssa.cirtwill@gmail.com\\
% +46 723 158464\\
 }

@@

@@

      Realistic values for n when k=0, based on a sample of 20 random sites:
      n=1: 0.25485794 0.02224566
      n=2: 0.22813413 0.01846427
      n=3:
      n=4:

@@

>>>>

\author{Dominique Gravel, \& Alyssa R. Cirtwill$^{1}$, Anna Ekl\"{o}f, Tomas Roslin, Kate Wootton}
\date{\small$^1$Department of Physics, Chemistry\\ 
and Biology (IFM)\\ 
Link\"{o}ping University\\
Link\"{o}ping, Sweden\\
% \medskip
% $^\dagger$ Corresponding author:\\
% alyssa.cirtwill@gmail.com\\
% +46 723 158464\\
 }

@@

      [[Checking this for reasonableness: sum is about 30, so we should have 30 galler-genotype combinations?]]

@@

      Realistic values for n when k=0, based on a sample of 20 random sites:
      n=1: 0.25485794 0.02224566
      n=2: 0.22813413 0.01846427
      n=3: 0.20648283 0.01555013
      n=4: 0.18858498 0.01326377

@@

  [[What if we have only one site? Can we use the number of observations of a pair of species interacting with any partners as the number of times they co-occur, and the number of interactions within the pair as k? This will be sort-of valid for insects but not for plants when researchers camp out by plant individuals... ]]
